\section*{Acknowledgments}

First and foremost, I would like to express my deepest gratitude to my family for their unwavering support and encouragement throughout this journey. To my loving girlfriend, Juliana, your patience and understanding have been my rock, and I could not have completed this work without you.

I am immensely grateful to my advisors, Pedro Dias and Ricardo de Camargo, for their invaluable guidance, insightful feedback, continuous support, and friendship. Your expertise and dedication have greatly enriched my research experience and have inspired me every day.

I would also like to acknowledge my former advisors, Renato Ramos da Silva, Roberto Carelli Fontes, and John Beardall, for their foundational support and mentorship during the early stages of my academic career.

A heartfelt thank you to my great friend Igor Gamella, who often acted as my programming mentor and provided invaluable support. Your guidance and assistance have been indispensable to my work.

To my colleagues, Matheus Bonjour, Renan Godoy, Maria Luiza Kovalski, Luis Andres Rodrigues, Rodrigo Tecchio, Victor Ranieri, and the entire MASTER team, thank you for your camaraderie and support. Your collaboration and friendship have made this journey enjoyable and rewarding.

I am also grateful for the technical support provided by Jean Peres, Djalma, Sebastião, and Samuca. Your help in resolving technical issues was crucial for the smooth progress of my research.

A special thanks goes to the researchers and professors who provided me with invaluable assistance: Carolina Gramcianinov, Pedro Peixoto, and Felipe Bragança Alves. Your advice and guidance have been instrumental in the completion of this work.

I would also like to extend my heartfelt thanks to the entire IAG community: professors, students, and staff. Your friendliness and support have made the IAG an incredible learning environment. Thank you for fostering a welcoming and stimulating atmosphere that has greatly enriched my academic journey.

I would also like to thank Karate-dō for teaching me discipline and hard work, as well as perseverance and resilience. Additionally, I am grateful to the ocean for also imparting lessons of perseverance and resilience. These lessons have been invaluable, and I will carry them with me throughout my life.

Finally, I would like to express my appreciation to Alexandra Elbakyan, Aaron Swartz, and the entire open-source community. Your contributions to the free and open access to knowledge have been invaluable to my research and burgeoning academic career.

\vfill

\begin{flushleft}
\rule{6cm}{0.5pt}\\
{\footnotesize{Esta tese/dissertação foi escrita em \LaTeX{} com a classe IAGTESE, para teses e dissertações do IAG.}}
\end{flushleft}